---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


step 1 result)
```{r}
library(classdata)
head(ames)
```
```{r}
summary(ames)
```
```{r}
colnames(ames)
```


As a team, we found that: The variables in the dataset Parcel ID, Address, Style,             Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea, Bedrooms, FinishedBsmtArea, LotArea, AC, FirePlace, Neighborhood. Variable types are int for many of the variables, boolean for things like FirePlace, and string for variables like address.The range can be seen in the summary block but the main vairable sale price goes from 0 to 20500000.    


step 2 result)

Our variable of interest, or main variable, is Sale Price. We expect almost every variable is going to have a relationship with Sale Price.













step 3 result)













As a team, we found that:














step 4 result)






Jensen:







Logan:







Nina:








Sarah









