---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


step 1 result)
```{r}
library(classdata)
head(ames)
```
```{r}
summary(ames)
```
```{r}
colnames(ames)
```


As a team, we found that: The variables in the dataset Parcel ID, Address, Style,             Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea, Bedrooms, FinishedBsmtArea, LotArea, AC, FirePlace, Neighborhood. Variable types are int for many of the variables, boolean for things like FirePlace, and string for variables like address.The range can be seen in the summary block but the main vairable sale price goes from 0 to 20500000.    


step 2 result)

Our variable of interest, or main variable, is Sale Price. We expect almost every variable is going to have a relationship with Sale Price.





step 3 result)


```{r}
range(ames$`Sale Price`)

```
The range is from 0 too 20500000

```{r}
hist(ames$`Sale Price`)

```

As a team, we found that:
There is an extreme number of homes on the lower end of the sale price range, with a smaller number of homes with a larger sale price. This follows with what we see in ames with most of the homes being similar, with a small amount of them being much larger than others.















step 4 result)






Jensen:
```{r}
range(ames$`TotalLivingArea (sf)`, na.rm = TRUE)
hist(ames$`TotalLivingArea (sf)`)
```
The range of TotalLivingArea is (without cleaning) 6007. The largest value is 6007 and the smallest 0. 

Our histogram shows the distribution of TotalLivingArea to have an average of ~1500, with a lower frequency for LivingArea above 3000.
```{r}
library(ggplot2)
ggplot(ames, aes(x=`TotalLivingArea (sf)`, y=`Sale Price`)) +
  geom_point()
```
The scatterplot between TotalLivingArea and SalePrice is what I expected due to the number of other factors that relate to SalePrice. There is little to no relationship between TotalLivingArea and SalePrice. A home might have a larger TotalLivingArea but be in a worse area, causing the price to be similar to others. This doesn't explain the oddities we saw in (3) because the data is dispersed.









Logan:







Nina:
```{r}
range(ames$`Bedrooms`, na.rm=TRUE)

```
library(ggplot2)
hist(ames$Bedrooms)
#The range is from 0 to 10 for Bedrooms in homes. The majority is between 2-4 Bedrooms.
boxplot(ames$Bedrooms)
#The pattern varies largely but is primarily between 2-5 with outliers between 1 and 10.


Sarah









